Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-27 paper/sec-mva.tex
Updated cut-flow in the case of PU

In this section we study how the MVA results are modified
when the analysis is performed including significant PU.
%
The cut-based analysis and the subsequent
MVA optimization have been performed using the same
settings as in the case without PU.
%
In Table~\ref{table:cutflowMVA_PU} we provide the results
  at the end of the cut-based analysis,
  for the case with $\la n_{\rm PU}\ra=80$ with SK+Trim
  subtraction,
  as well as the post-MVA results for the
  corresponding optimal values of $y_{\rm cut}$.
  %
  Additionally we quote in
  both cases the number of signal and
    total background events expected
    at the HL-LHC with $\mathcal{L}=3$ ab$^{-1}$
    and the values of $S/\sqrt{B}$ and $S/B$

@@

Once the MVA is applied, the signal significance in the 
resolved, intermediate and boosted
categories increases to 4.6, 4.1 and 3.7 respectively,
to be compared with the corresponding values
without PU, namely 4.5, 4.8 and 5.4.
%
Therefore, the post-MVA effect of PU on $S/\sqrt{B}$ is
a moderate degradation of the boosted and intermediate categories,
while the resolved category is largely unchanged.
%
We also observe that, due
to the MVA, the
signal over background ratio is increased from 0.02\%, 0.08\% and
0.2\% up to 1\%, 4\% and 2\% in the resolved, intermediate
and boosted categories respectively.
%
This indicates that while this measurement is still highly challenging,
requiring a careful extraction of the QCD
background from the data, it is certainty within reach.

>>>>

In this section we study how the MVA results are modified
when the analysis is performed including significant PU.
%
The cut-based analysis and the subsequent
MVA optimization have been performed using the same
settings as in the case without PU.
%
In Table~\ref{tab:cutflow_PU80_1}
we provide the pre-MVA cut flow in the case of PU,
the corresponding version without PU is
Table~\ref{tab:cutflow_noPU_1}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \scriptsize
      \input{table_PU80.tex}
    \caption{\small Same as Table~\ref{tab:cutflow_noPU_1}
for the case  now for the case
    of PU+SK+Trim with $\la n_{\rm PU}\ra=80$.
 \label{tab:cutflow_PU80_1}}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In Table~\ref{table:cutflowMVA_PU} we provide the results
  at the end of the cut-based analysis,
  for the case with $\la n_{\rm PU}\ra=80$ with SK+Trim
  subtraction,
  as well as the post-MVA results for the
  corresponding optimal values of $y_{\rm cut}$.
  %
  Additionally we quote in
  both cases the number of signal and
    total background events expected
    at the HL-LHC with $\mathcal{L}=3$ ab$^{-1}$
    and the values of $S/\sqrt{B}$ and $S/B$

@@

Once the MVA is applied, the signal significance in the 
resolved, intermediate and boosted
categories increases to 4.6, 4.1 and 3.7 respectively,
to be compared with the corresponding values
without PU, namely 4.5, 4.8 and 5.4.
%
Therefore, the post-MVA effect of PU on $S/\sqrt{B}$ is
a moderate degradation of the boosted and intermediate categories,
while the resolved category is largely unchanged.
%
We also observe that, due
to the MVA, the
signal over background ratio is increased from 0.02\%, 0.08\% and
0.2\% up to 1\%, 4\% and 2\% in the resolved, intermediate
and boosted categories respectively.
%
This indicates that while this measurement is still highly challenging,
requiring a careful extraction of the QCD
background from the data, it is certainly within reach.
